A dataset of Scratch programs,\\Scraped, Shaped and Scored

### 2017-02-17 MSR-Scratch.tex
Shortened conclusions

\section{Conclusion}
The increasing popularity of Scratch as an introductory programming language makes it an increasingly popular research target in the computing education research field.
This paper presented an open and timely dataset of recent Scratch programs, that can facilitate research in the fields of source code analysis and computing education.
The dataset can support various research topics, including the ones related to the assessment of the programming skills that novice programmers develop in the Scratch environment and the exploration of their learning progressions, and issues related to the quality of the programs and the identification of smells and bad programming habits.

The dataset contains 250 thousand Scratch projects, from more than 100 thousand different users, that were scraped from the Scratch project repository.
It is made available as a database\footnotemark[\ref{dataseturl}] which includes the source code of the Scratch projects, their metadata, and their programming mastery scoring results.

>>>>

\section{Conclusion}
We presented a dataset of recent Scratch programs scraped from the Scratch project repository.
It is made available as a database\footnotemark[\ref{dataseturl}] which includes the source code of the Scratch projects, their metadata, and their programming mastery scoring results.
The dataset can facilitate research in software engineering and computing education, for topics like the assessment of the programming skills that novice programmers develop, the exploration of their learning progressions, and issues related to the quality of the programs and the identification of smells and bad programming habits.
